Multi-line Intensity Mapping

### 2019-06-20 paper/ms.tex
Add technical background section, average intensity

>>>>

\section{Technical Background}\label{sec:tech_back}
We first lay out the approach to modelling the average intensity of an
arbitrary emission line, the spatial clustering of that signal, the
cross-spectrum between two different lines, and the fisher matrix approach for
estimating the bias factors from an arbitrary number of cross-spectra or
cross-spectra and auto-spectra.

\subsection{Intrinsic Line Emission}\label{ssec:line_emission}
The average intensity of an arbitrary line is calculated according
to the simple model of \citet{2016ApJ...825..143L}, which is based upon
\citet{2011ApJ...741...70L} and {\bf Pullen 2013}. The details are laid out in
Appendix~\ref{app:co_int}, but in brief the model assumes a {\bf Schechter
1976} form for the star formation rate function and a linear relationship
between a halo's luminosity and its star formation rate with constants of
proportionality from \citet{2010JCAP...11..016V}.

We note that in this model the redshift evolution of each line is identical up
to the luminosity-SFR constant of proportionality. In reality, we do not
expect this to be the case. For example, the different CO lines should have
varying intrinsic strengths since the typical phase of the ISM in each
emitting galaxies should change as a function of redshift. This highlights one
of the limitations of the line intensity model adopted here. Fully
understanding the underlying galactic population will require more nuanced
models, though the best path forward is not clear.
